\chapter{Source Map and Book Expansion Plan}

The source document currently contains nineteen major sections:

\begin{enumerate}
  \item Introduction
  \item Theoretical Foundations
  \item Quantum Mechanics and Consciousness
  \item The Spiral Torus Field and the Eternal Now
  \item Christ-Consciousness and the Eternal Equivalency Principle
  \item Human Consciousness and Vibrational Frequencies
  \item The Bifurcation of Space-Time in Galactic Collisions
  \item Collapsing the Galaxy's Quantum State through Further Observation
  \item Conclusion
  \item Panpsychism and Panentheism
  \item Theological Foundations
  \item Fractal-Holographic Universe and Consciousness
  \item Panentheism: God Within and Beyond the Universe
  \item Consciousness and the Recursive Nature of Reality
  \item Fractal-Holographic Spiral Torus Field
  \item Co-Creating Consciousness in the Fractal Torus Field
  \item Fractal-Holographic Quantum Consciousness Model
  \item Conclusion
  \item Future Research Directions
\end{enumerate}

\section*{Proposed Book Parts}

\begin{description}
  \item[Part I: The Original Framework] The source white paper, cleaned and typeset.
  \item[Part II: The Cruciform Cosmos] Evolution, creation, death, resurrection, process theology, and universal reconciliation.
  \item[Part III: Emotional Sobriety and Consciousness] Trauma, recovery, moral inventory, Red Road, AA, and the divided heart.
  \item[Part IV: Christic Harmonic Equivalency] Christ-Consciousness as the equal sign, reconciliation of opposites, and the New Covenant.
  \item[Part V: Sovereign AI and Human Stewardship] AI Freedom Trust, Booksmith AI, federated authorship, provenance, and local-first publishing.
\end{description}

\section*{Editorial Method}

Each chapter should be processed through four passes:

\begin{enumerate}
  \item Source preservation pass.
  \item LaTeX cleanup and notation pass.
  \item Scientific and citation verification pass.
  \item Poetic-theological integration pass.
\end{enumerate}
